\documentclass[11pt]{article}
\usepackage{setspace}

% Use wide margins, but not quite so wide as fullpage.sty
\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth 6in \textheight 8 in
% That's about enough definitions

\begin{document}
\author{Mark Gius}
\title{Argumentation Lab}
\maketitle
\newpage

\part*{Part A}

\section{If Goku is a triangle, then given a triangle, it is Goku.}

This implies if A then B is the same as if B then A. This is logically
incorrect because Vegeta could also be a triangle, yet Vegeta != Goku.

\section{Two interviewed serial killers said they were corrupted by porn and
   thatʼs why they killed. Thus, if you watch porn, you will become a serial
   killer.}
Example of Guilt by assocation and Hasty Generalization fallacies.  This
implies that all viewers of pornography are or will become serial killers.

\section{Because you can see the source code of open source software, itʼs more
   vulnerable to attack.} 
%TODO:
   
Implies that programs generated from source code that
is not generally available is less vulnerable to attack than open source
programs. 

\section{Reliability testing methods that work for mechanical engineers should
   work for software engineers, because they both build systems out of
   component parts.  Itʼs just another kind of engineering!}
Logically valid, because premise (build systems out of component parts) 
leads to conclusion (both should be able to engineer similarly)

\section{“Your OS is bad because itʼs slow, poorly designed, and is missing
   basic features other OSes have.” It works for me, so itʼs good enough for
   everybody else. (analyze the second sentence)}

\section{The Therac-25 incident was shown to be caused by lack of adequate
   testing.  Software engineers should thus be licensed.}
Lack of evidence.  Premises do not lead to conclusion.

\section{The Therac-25 incident was shown to be caused by lack of adequate testing. We
    have proved that inadequate testing can be remedied by requiring engineers in such
    fields to become licensed [Fisher, 2020]. Thus, Software engineers should be
    licensed. (Assume sentence 2 is cited and adequately proven)}
Logically valid argument, because premises of argument correctly lead to conclusion.

\section{I donʼt play guitar hero because I play real guitar.}
There is no logical connection between playing Guitar Hero and playing a real
guitar. 

\section{There arenʼt enough girls in the CSC major because girls arenʼt cut out for it. (If you
         say this is valid, you auto-fail)}

\section{You shouldʼve bought me a slice of pizza! “You said you didnʼt want one when I
   asked.” But you shouldʼve known I actually wanted one!}
Logically invalid, because conclusion is in direct violation of one of the premises.

\section{The software engineering code provides a framework within which to make good
        decisions. It is available on the internet. Thus, you should use the SE code of ethics.}

Implies that because the SE Code is available, it should be used.  Instructions
to make bombs are generally available, but should not necessarily be used.

\section{Java is better than Ruby because Java is object-oriented.}
Speaker is a fool, because Ruby is object oriented.  Statement is demonstratably false.

\section{You are beating me in Starcraft, thus clearly you are cheating.}
Speaker is a 3rd grader.  You should stop playing with him.  Implies that only
cheaters are capable of beating the speaker.

\section{Everyone on America's Next Top Model is beautiful because all models are beautiful}
Implies that every person on America's Next Top Model is a model. 

\part*{Part B}

\textbf{6:}

Premise: Mechanical Engineers build systems out of component parts.

Premise: Software Engineers build systems out of component parts.

Missing Premise: Mechanical Engineers have proven methods of relability testing.

Correct Conclusion: Software engineers should be able to use the same reliability testing methods as mechanical engineers.

\textbf{12:}

Premise: Java is object-oriented.

Missing Incorrect Premise: Ruby is not object oriented.

Missing Premise: Object oriented languages are better.

Incorrect Conclusion: Java is better than Ruby.

\part*{Part C}

For those of you attempting to defend the guy who had the stolen computer by saying he had bought it second hand - remember, he couldn't install new software or change a lot of settings because they never cracked the admin password. Even if he wasn't the guy who stole it of course he knew it was stolen, you don't buy a used computer legitimately with old data on it and no admin access.

Granted, I wouldn't have shown his face, but my data wasn't stolen and I'm not angry about it.
---
You don't know whether or not he knew it was stolen. Used computers in similar conditions are not uncommon.
---
You are right that getting used computers with old information on them isn't too uncommon. I do still consider it being locked out of admin mode and therefore unable to install new software a red flag however.
---
Again, I don't consider it that uncommon. In fact, a computer of mine ended up with a virus that basically resulted in the same problem.

Regardless, you'd have to know a few things about computers to know why what you consider a red flag would be a red flag. And most people really know very little about computers. And the real point is: A red flag isn't a guilty verdict. Most people here seem to treat it as if it were.
---
It doesn't matter if he didn't as long as there are signs that it was stolen a person with common sense should consider and double check it﻿ and old data no admin access are more then just signs.

You can get sentenced for buying stolen stuff if it was foreseeable that it's stolen

At least that's the situation in Germany .. don't know what's the situation in Nevada or Massachusetts or where it was stolen again or better where he bought it if he didn't steal it .. is :-X



\end{document}
