\documentclass[12pt]{article}

\usepackage{fullpage} % does reasonable things
\usepackage{setspace} % allows double spacing
\usepackage{url}

\begin{document}
\author{Mark Gius}
\title{Job Fair Lab}
\maketitle

\section{Job Fair Option A}

\doublespacing

I did not go into the job fair with the intention of fulfilling option A, but during the CBS Interactive talk their representatives asked us to ask them anything and ``pull no punches,'' so I went for it.  One of their representatives was from GameSpot's Advertising Sales division, so I went ahead and asked her about the GameSpot Kane and Lynch 2 controversy from last year \footnote{\url{http://en.wikipedia.org/wiki/Gamespot#Gerstmann_dismissal}}.  My question was, as best I can remember it, ``At GameSpot, your advertisers are largely the game companies whose games you are reviewing.  There's a reasonably good chance that a game that has just purchased ad space is about to get panned in a review.  How do you deal with the potential conflict of interest in this situation?'' The representative was familiar with the case (although I didn't mention Kane and Lynch until requested), and spoke about how the sales team and the review/content teams are intentionally kept away from each other.  It sounded like the review team had the ability to inform the sales team of impending decisions about games and other content on the site so that the sales team can inform and work with the advertisers so that they don't feel as though they had been hoodwinked.  It's hard to say how much of the answer was legitimate, although it sounds as though the separation between Sales and and the Review team was in place at the time, thus the massive advertising push for Kane and Lynch right around the time that a severely critical review was published.

\singlespacing

\section{Job Fair Option B}

\doublespacing
I currently work for Createspace, a local subsidiary of Amazon.com.  In general, I can only speak for Createspace, not Amazon as a whole. Createspace does not adhere to the ACM SE Code of ethics explicitly, although ethical behavior is expected at the company and most aspects of the SE Code are strongly present in the workplace.  

In particular, I have been present numerous times where projects have begun to run over budget or have privacy or technical implications that our ``clients'' may not be aware of, very similiar to the expectations of SE Code 2.06.  I was recently part of a project that was planning on storing the username/password of an end-user for a third-party without informing the end-user.  I fought strongly against that decision on privacy and technical reasons.  Due to technical reasons having to do with the third-party systems, we ended up having to store the username (which I was fine with) and we now inform the end-user of that fact when they provide the username and password for the third-party to us.  I received full support from my coworkers and eventually the business interests on this point.

Createspace has a strong aherence to the principle of maintainence as new development, as per SE Code 3.15.  In my daily doings at Createspace, the difference between new features and bug fixes is primarily one of scope: bug fixes tend to be smaller than new features.  Otherwise, bugs are treated to the same development process as new features: testing, code review, and release process are consistent throughout.

Createspace --- and from what I have heard, Amazon as well --- practically breathes SE Code 7.02: assisting in the development of colleagues.  In fact, it's part of Amazon's corporate governance \footnote{\url{http://phx.corporate-ir.net/phoenix.zhtml?c=97664&p=irol-govHighlights}} to ``focus on hiring and \emph{retaining} versatile and talented employees'' (ephasis mine).  Team swapping is supposed to be a common practice at Amazon, with various teams often hiring from other subsidiaries and teams to bring in proven talent that is excited about the work and product.  Last spring I mentioned to my manager that I was interested in switching from the Systems Administration team to a Development role so that I could get some experience there before I graduated.  My manager was sad to see me leave his team, but the transition process was started almost immediately and by the next quarter I was a developer.

Createspace has strict hiring standards --- the company was founded by Clint Staley, and he is well known for high standards --- so I am not aware of any (intentional) violations of any ethical standards at the company.  I have been present when \emph{potential} violations may or may not have taken place, and the handling of even a \emph{potential} leak of customer info or content is treated with the highest amount of focus and attention from nearly everyone in the company.

Amazon provides an anonymous phone number that can be called to report ethics violations.  I've never called it and I don't know anyone that has.  

\end{document}
