\documentclass[12pt]{article}
\usepackage{setspace}

% Use wide margins, but not quite so wide as fullpage.sty
\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth 6in \textheight 8 in
% That's about enough definitions

\begin{document}
\author{Mark Gius}
\title{Future Me Lab}
\maketitle
\newpage
%
%The future you lab is a simple personal statement of goals and interests with a projection into the next 10 years. Imagine youʼve graduated from Cal Poly with the degree you are interested in, you find the job or the direction you truly want, and you build the sort of life you truly want.
%
%The document should be 1 – 2 pages in length and should be typewritten in a professional manner, so that it is easily read.
%
%You may also approach this Lab as an “obituary” that youʼd like to see written for you when you pass, after your life has gone the way you would like it to.
%
%\newpage
\doublespacing

Ten years down the road it is my plan to be employed in a programming or software engineering type position where I primarily work on backend features and code.  I have absolutely no interest whatsoever in user interface design and my ideal position is one that the end-user doesn't even realize exists.  I don't have any particular desire to work for a specific company, although I will avoid companies that appear to make short-sighted and greedy decisions that harm the overall state of computing.  The company I work for should consider the product they are creating to be important to furthering the state of the art.  My company will also be interested in more than making money.  My coworkers will be prone to arguments that further our knowledge of computing.  It would be a common weekly occurrence to have a long discussion about language features or new programming development even if the topic of discussion in inapplicable to our work.  

I see myself heavily involved in the local Linux Users Group where I live, helping to promote the cause of open source software in my community.  In addition to helping users who come to us, I would seek to increase the presence of Linux and other open source software in my community by attempting to promote its use in local schools and businesses.  I see myself volunteering with local schools to provide a programming learning experience for students with an interest in computers, thus making up for my dismal computing experience in my pre-collegiate education.

My home will be fairly spartan, as I have no desire for decorations.  For years now the walls of my living spaces have been bare and my desk has been populated only by computing hardware and my current work.  Although traditional home decorations may be lacking, my home will have a "wicked awesome" home-entertainment system.  This sytem will be linux-based, of course. 

Ending on a lighter note, I will have become a moderately competent chef, able to prepare meals to impress and delight friends and family on special occasions.  This will go a long way towards impressing my wife (fingers crossed) or stream of eligible bachelorettes that shall inevitably cross my path. 

\end{document}
